Cluster Difference Imaging Photometric Survey. III. An Open Cluster Spanning 500\,Parsecs

### 2021-03-16 cluster_paper/ms.tex
update ms

\title{
  Cluster Difference Imaging Photometric Survey. III.
  %The Coeval Core \& Halo of NGC\,2516
  %The Halo of NGC\,2516 Extends To At Least 300\,pc
  %An Open Cluster With a 300\,pc Halo
  An Open Cluster Spread Across 500\,pc
  %NGC\,2516  300\,pc
}

@@

% NB. the "classical tidal radius" is from e.g., Piskunov+08 or
% Kharchenko+2013. The latter givs a radius r2 of 0.71 degrees. At 380
% pc, corresponds to 4.7pc. The King tidal radius given by K13 is
% 7.70pc.
\begin{abstract}
  Recent analyses of the Gaia data have reported the existence of
  diffuse stellar populations surrounding nearby open clusters. 
  The stars in these diffuse halos could be tidal escapees from the
  cluster cores, or they could be remnants of an initially dispersed
  star formation complex.
  They could also be field stars---the false positives of overly
  sensitive clustering algorithms.
  In this study, we focus on a halo with a tip-to-tip length of
  $\approx$500\,pc reported around the $\approx$150\,Myr open cluster
  NGC\,2516.
  The classical tidal radius of the cluster is $\lesssim$10\,pc.
  Combining photometry from Gaia, rotation periods from TESS, and
  lithium measurements from Gaia-ESO and GALAH, we find that the halo
  of NGC\,2516 is real and coeval with the core.
  Two in three kinematically selected halo members out to 250\,pc from the
  cluster center show rotation periods consistent with a
  gyrochronological age of 150\,Myr.
  A comparison sample of field stars shows no such trend.
  The rotation period and lithium abundances of the cluster stars are
  also anti-correlated at fixed stellar mass, as has been observed in
  similar stellar populations.
  This work quantifies the degree to which Gaia-based
  analyses can identify dispersed stellar populations against a
  background of field star contaminants, and
  expands the set of confirmed NGC\,2516 members by a factor
  of $\approx$2.
  We highlight the implications for spectroscopic survey targeting,
  open cluster dispersal, and planet searches around young stars.
\end{abstract}

@@

We analyzed X, Y, Z.
Our main results are as follows.
\begin{itemize}
	\item 
\end{itemize}

>>>>

\title{
  Cluster Difference Imaging Photometric Survey. III.
  %The Coeval Core \& Halo of NGC\,2516
  %The Halo of NGC\,2516 Extends To At Least 300\,pc
  %An Open Cluster With a 300\,pc Halo
  An Open Cluster Spanning 500\,Parsecs
  %NGC\,2516  300\,pc
}

@@

% NB. the "classical tidal radius" is from e.g., Piskunov+08 or
% Kharchenko+2013. The latter givs a radius r2 of 0.71 degrees. At 380
% pc, corresponds to 4.7pc. The King tidal radius given by K13 is
% 7.70pc.
\begin{abstract}
  Recent analyses of the Gaia data have reported the existence of
  diffuse stellar populations surrounding nearby open clusters. 
  The stars in these diffuse halos could be tidal escapees from the
  cluster cores, or they could be remnants of an initially dispersed
  star formation complex.
  They could also be field stars---the false positives of overly
  sensitive clustering algorithms.
  In this study, we focus on a halo with a tip-to-tip length of
  $\approx$500\,pc reported around the $\approx$150\,Myr open cluster
  NGC\,2516.
  The classical tidal radius of the cluster is $\lesssim$10\,pc.
  Combining photometry from Gaia, rotation periods from TESS, and
  lithium measurements from Gaia-ESO and GALAH, we find that the halo
  of NGC\,2516 is real and coeval with the core.
  Two thirds of kinematically selected halo members out to 250\,pc from the
  cluster center have rotation periods consistent with a
  gyrochronological age of 150\,Myr.
  A comparison sample of field stars shows no such trend.
  In addition, the lithium abundances of stars in the halo are
  elevated relative to the field, and are correlated with the stellar
  rotation rate in a manner consistent with previous observations of the
  Pleiades and Psc Eri.
  This work expands the set of confirmed NGC 2516 members by a factor
  of two, and is consistent with a paradigm in which the halos of many
  open clusters are more populous than their cores.
  We highlight the implications for spectroscopic survey targeting,
  open cluster dispersal, and planet searches around young stars.
\end{abstract}

@@

The combination of Gaia, TESS, and the GALAH and Gaia-ESO
spectroscopic surveys has clarified a few 
things about \cn.
\begin{itemize}
	\item {\it Overdensities observed by Gaia in five-dimensional (3-D position + 2-D velocity)
		phase space
		revealed a halo of stars spanning 500 parsecs in the plane of the galaxy.}
	The earlier reference to the full structure that we can find is by CITE KOUNKEL.
	The halo is more precisely described as a leading and trailing tail
	(Figure~\ref{fig:XYZ}), with the leading end on the interior of the
	cluster's
	galactic orbit.
	%
	\item {\it Isochronal, rotational, and lithium age-dating show that the halo is real and coeval with the core of \cn.}
    The Gaia EDR3 photometry and astrometry show a main-sequence turnoff consistent with
    an isochronal age of 150\,Myr for both the core and halo.
    The faintest M dwarfs in the core and halo are also elevated relative to a field star comparison sample, but using
    this to isochronally measure the age is challenging due to uncertainties in M dwarf atmospheric opacities.
    Gyrochronally, FIXME FIXME FIXME
    %
    \item {\it The identified halo extends to $\approx$250\,pc in separate from the cluster center, and out to $\approx$5\kms\ in velocity separation.}
    Figure~\ref{fig:physical_x_rotn} shows the overlap between kinematic
    and rotational cluster members. 
    %
    \item {\it The field star contamination rate increases at larger physical and 
    velocity separations from the cluster core.}
	Figure~\ref{fig:physical_x_rotn}

    The stars further from the c
    As a reminder, a star with a 1\kms\ velocity difference moves 1\,pc per Myr.

	More specifically, ``two thirds of kinematically selected halo members out to 250 pc from the cluster center have rotation periods consistent with a gyrochronological age of 150 Myr''.

	\item {\it Differential rotation in the Milky Way likely plays an important role in shaping the halos of nearby open clusters.}
	The Milky Way's differential rotation rate has a comparable
	order of magnitude ($\approx$-0.2\,deg\,Myr$^{-1}$\,kpc$^{-1}$) to that measured across the halo \citep{meingast_2021}.
	It therefore likely plays an important role in understanding the halo's formation.

\end{itemize}
